### 2010-01-22 trunk/deliverables/D2_4_Mediation/fast_d2_4_2_mediation.tex
Added newest version of USGS article contents
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@442 d8b0c59b-6544-0410-94d9-83a5658a058e
Final rough version before Albert's contribution (still needs a final read-through)
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@448 d8b0c59b-6544-0410-94d9-83a5658a058e

@@

\section{Introduction} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:introduction}
\paragraph{Goal and Scope.}
FAST is a visual programming platform allowing business users to build enterprise-class mashups, employing various underlying services and generating new ones. Resources in FAST are described semantically using different ontologies and vocabularies, and can therefore be combined to what we can call ``intelligent gadgets''. In the services created within the FAST environment, the ontologies come from different parties involved in the creation of gadgets and building blocks. These ontologies, though different, will sometimes cover the same domain, making ontology matching necessary, as the means to reconcile differences in the various conceptualisations.

@@

\paragraph{Structure of the Document.}
Part \ref{part:d2.4.2} describes the approach of integrating ontology matching into the FAST environment. 
%Describe the rest.
Part \ref{part:d2.4.1} contains the first iteration of this document, D2.4.1, laying down the theoretical foundations of ontology matching. We discuss ontologies in general in Section \ref{sec:ontologies}, present the ontology mediation problem in Section \ref{sec:mediationproblem} , discuss the types  of mismatches between ontologies in Section \ref{sec:ontologymismatches} and detail the main approaches to ontology mediation in Section \ref{sec:mediationapproaches}.

@@

\part{D2.4.1: Theoretical Foundations for Ontology Mediation}
\label{part:d2.4.1}
%\include{fast_d2_4_2_part2}

@@

In this second iteration we established the approach to integrate ontology matching into FAST, and have shown the implementation details as well as test scenarios. We have presented a tool for finding the alignments between ontologies, as well as a powerful language to represent them, beyond the capabilities of the tool. We have shown how this matching is done at the different phases of the gadget life cycle and the approach taken at every level.

We plan to evaluate the feasibility of ontology matching in real-life tests and finalize it for the completed version of the FAST platform.

>>>>

\usepackage{listings} %source code listings
\usepackage{paralist}
\usepackage{booktabs}

@@

\section{Introduction} %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\label{sec:intro}
\paragraph{Goal and Scope.}
FAST is a visual programming platform allowing business users to build enterprise-class mashups, employing various underlying services and generating new ones. Resources in FAST are described semantically using different ontologies and vocabularies, and can therefore be combined to what we can call ``intelligent gadgets''. In the services used within the FAST environment, the ontologies involved in the creation of gadgets and building blocks come from different parties. These ontologies, though different, will sometimes cover the same domain, making ontology matching necessary, as the means to reconcile differences in the various conceptualisations.

@@

\paragraph{Structure of the Document.}
Part \ref{part:d2.4.2} describes the approach of integrating ontology matching into the FAST environment. Section \ref{sec:overview} gives the big picture of ontology matching in fast, which the remaining three sections expand. Thus, Section \ref{sec:ontologyengineering} describes a tool to automatically discover alignments, a scenario and example ontologies to demonstrate the capabilites of the tool, and the testing procedure with the results.  The remaing part of the section deals with a tool to define the discovered mapping rules in a way that is consistent with other similar tasks within the FAST platform, and describes the way in which matching operators are stored within the Semantic Catalogue. Section \ref{sec:gadgetbuilding} shortly describes the way the matching operator is used when composing screenflows and Section \ref{sec:runtime} describes how the matching operator and the defined rules are converted and used in the final, deployed gadget.

%Describe the rest.
Part \ref{part:d2.4.1} contains the first iteration of this document, D2.4.1, laying down the theoretical foundations of ontology matching. We discuss ontologies in general in Section \ref{sec:ontologies}, present the ontology mediation problem in Section \ref{sec:mediationproblem} , discuss the types  of mismatches between ontologies in Section \ref{sec:ontologymismatches} and detail the main approaches to ontology mediation in Section \ref{sec:mediationapproaches}.

@@

\part{D2.4.1: Theoretical Foundations for Ontology Mediation}
\label{part:d2.4.1}
\include{fast_d2_4_2_part2}

@@

In this second iteration we established the approach to integrate ontology matching into FAST, and we have shown how this matching is done at the different phases of the gadget life cycle and the approach taken at every level. Firstly, have shown the implementation details as well as test scenarios, we have presented a tool for finding the alignments between ontologies as well as a powerful language to represent them, we have described a tool to compose mapping rules in a consistent manner with other FAST components and the means to save them in the Semantic Catalogue. Secondly, we described the way in which mapping operators are used in the GVS to combine discrepant screens. Lastly, we presented the way the matching operator and mapping rules are deployed and exploited in the JavaScript gadget.

For the last and final iteration of deliverable D2.4 we plan to evaluate real-life scenarios and finalize the implementation of ontology matching for the FAST platform.

### 2010-01-22 trunk/deliverables/D2_4_Mediation/fast_d2_4_2_part1.tex
Final rough version before Albert's contribution (still needs a final read-through)
git-svn-id: https://svn.forge.morfeo-project.org/fast-fp7project@448 d8b0c59b-6544-0410-94d9-83a5658a058e

\section{Overview}
\subsection{Ontology Matching}
\label{mediation}

@@

\section{Ontology Engineering Phase}

@@

\section{Gadget Building Phase}
Every time ontology matching is performed and an alignment is created between two underlying resources, the corresponding alignment rules are stored and an operator is created in the catalogue.

@@

\section{Runtime} 
At runtime, the matching operator's rules are tranformed into JSON data used by the JavaScript gadget. Thus, when data come from the two disparate resources, the gadget will automatically transform data instances of the ontology belonging to the first resource, into instances of the ontology belonging to the second resource.

>>>>

\section{Overview}
\label{sec:overview}

\subsection{Ontology Matching}
\label{mediation}

@@

\section{Ontology Engineering Phase}
\label{sec:ontologyengineering}

@@

\section{Gadget Building Phase}
\label{sec:gadgetbuilding}
Every time ontology matching is performed and an alignment is created between two underlying resources, the corresponding alignment rules are stored and an operator is created in the catalogue.

@@

\section{Runtime} 
\label{sec:runtime}
At runtime, the matching operator's rules are tranformed into JSON data used by the JavaScript gadget. Thus, when data come from the two disparate resources, the gadget will automatically transform data instances of the ontology belonging to the first resource, into instances of the ontology belonging to the second resource.
